03_datawrangle

### 2020-05-12 analysis/01_limma_all.Rmd
working on large limma files

knitr::opts_chunk$set(fig.path = '../figures/01_limma/',cache=TRUE)
```

@@

```{r read}
# import "colData" which contains sample information and "countData" which contains read counts
colData <- read.csv("../metadata/00_samples.csv", header = T, row.names = 1)
countData <- read.csv("../results/00_counts.csv", header = T, row.names = 1)
head(colData)
geneinfo <- row.names(countData)
```

@@

```{r edgeR}
# create a large DGEList with 3 elements
parentalobject <- DGEList(counts=countData, genes=geneinfo, group=colData$group)

@@

write.csv(parentalobject$pseudo.counts, "../results/01_pseudo.counts.csv")
```

>>>>

knitr::opts_chunk$set(fig.path = '../figures/01_limma/')
```

@@

```{r read}
# import "colData" which contains sample information and "countData" which contains read counts
colData <- read.csv("../metadata/00_colData.csv", header = T, row.names = 1)
countData <- read.csv("../results/00_counts.csv", header = T, row.names = 1)

#countData  <- head(countData, 1000) # suset for quick analysis

geneinfo <- row.names(countData)
```

@@

```{r edgeR}
head(colData$group)
# create a large DGEList with 3 elements
parentalobject <- DGEList(counts=countData, genes=geneinfo, group=colData$group)

@@

write.csv(parentalobject$pseudo.counts, "../results/01_limma.csv")
```

### 2020-05-12 analysis/03_datawrangling.Rmd
slimming data prep
working on large limma files

Note, pseudocounts is too big for storage on github :(

```{r}
pseudocounts <- read_csv("../results/01_pseudo.counts.csv")
head(pseudocounts[1:3])
pseudocounts <- as.data.frame(pseudocounts)
row.names(pseudocounts) <- pseudocounts$X1
pseudocounts$X1 <- NULL
# prep count data for all samples
pseudocounts <- as.data.frame(t(pseudocounts))
head(pseudocounts[1:3])

pseudocountsLong <- pseudocounts %>%
  mutate(samples = row.names(.)) %>%
  pivot_longer(-samples, names_to = "gene", values_to = "pseudocounts")
#pseudocountsLong$samples <- row.names(pseudocountsLong)
head(pseudocountsLong)
```

@@

```{r}
colData <- read.csv("../metadata/00_samples.csv", header = T, row.names = 1)
colData$treatment <- factor(colData$treatment, levels = alllevels)
colData <- colData %>% mutate(tissue = fct_recode(tissue, "gonads" = "gonad"))
colData$tissue <- factor(colData$tissue, levels = tissuelevels)
row.names(colData) <- colData$V1

# check ready for analysis
# row.names(countData) == row.names(colData)
head(row.names(pseudocounts) == row.names(colData))
```

@@

```{r}
# all genes in this parental care dataset 
geneids <- read_csv("../metadata/00_geneinfo.csv") %>%
  select(-X1) %>%
  rename("NCBI" = "entrezid",
         "gene" = "Name")

>>>>

Note, limmacounts is too big for storage on github :(

```{r}
limmacounts <- read_csv("../results/01_limma.csv")
head(limmacounts[1:3])
limmacounts <- as.data.frame(limmacounts)
row.names(limmacounts) <- limmacounts$X1
limmacounts$X1 <- NULL
# prep count data for all samples
limmacounts <- as.data.frame(t(limmacounts))
head(limmacounts[1:3])

limmacountsLong <- limmacounts %>%
  mutate(samples = row.names(.)) %>%
  pivot_longer(-samples, names_to = "gene", values_to = "limmacounts")
#limmacountsLong$samples <- row.names(limmacountsLong)
head(limmacountsLong)
```

@@

```{r}
colData <- read.csv("../metadata/00_colData.csv", header = T, row.names = 1) %>%
  mutate(treatment = factor(treatment, levels = alllevels),
         tissue = factor(tissue, levels = tissuelevels))
colData <- as.data.frame(colData)
row.names(colData) <- colData$V1

# check ready for analysis
# row.names(countData) == row.names(colData)
head(row.names(limmacounts) == row.names(colData))
```

@@

```{r}
# all genes in this parental care dataset 
geneids <- read_csv("../metadata/00_geneinfo.csv") %>% select(-X1)
